### 2016-11-04 Paper_v8.tex
JB tweaks

NF-$\kappa$B may also play an essential role of in the epithelial transformation.
NF-$\kappa$B may influence Snail expression through the AKT pathway and directly stabilize Snail activity \cite{Wu:2009cr}.  This is particularly important for integrating inflammation pathways, such as interleukin-6 (IL-6) and tumor necrosis factor-$\alpha$ (TNF-$\alpha$), which have been linked to EMT in pathological conditions \cite{Sullivan:2009bh}.
Other pathways such as Notch have also been shown to act synergistically with TGF-$\beta$ to express Slug in the developing embryo \cite{Niessen:2008nx}.
In addition, other regulatory proteins such as ZEB1 could be added to the next generation model.
ZEB1 can activate the expression of mesenchymal genes such as collagens, smooth muscle actin and myosin, Vimentin while simultaneously contributing
to the repression of epithelial genes \cite{Liu:2008aa}.
Thus, ZEB1 can act in parallel to SNAIL and thus be an alternative to the canonical signaling paradigm presented here.
Hong et al. developed an ODE model of ZEB1 signaling in MCF10A cells which also demonstrated intermediate EMT states \cite{Hong:2015aa}.
However, given that we do not have ZEB1 in our model architecture, this suggests multiple types of hybrid phenotypes could exist within the EMT program.
Lastly, while we have modeled classical protein signaling, we have not considered the role of regulatory RNAs on EMT.
There is growing evidence that microRNAs (miRNAs) play a strong role in EMT, where several miRNAs,
for example miR-21 and miR-31 are strongly associated with TGF-$\beta$ exposure \cite{Bullock:2012aa}, and have suggested that
the EMT process is driven by a miR-34/SNAIL and/or miR-200/ZEB feedback circuit \cite{Lu:2013aa,Zhang:2014aa,Tian:2013aa}.
Addressing missing structural components like these (and potentially others), could generate more insight into TGF-$\beta$ signaling and its role in phenotypic transformation.

>>>>

NF-$\kappa$B may also play an essential role of in the epithelial transformation.
NF-$\kappa$B may influence Snail expression through the AKT pathway and directly stabilize Snail activity \cite{Wu:2009cr}.  This is particularly important for integrating inflammation pathways, such as interleukin-6 (IL-6) and tumor necrosis factor-$\alpha$ (TNF-$\alpha$), which have been linked to EMT in pathological conditions \cite{Sullivan:2009bh}.
Other pathways such as Notch have also been shown to act synergistically with TGF-$\beta$ to express Slug in the developing embryo \cite{Niessen:2008nx}.
In addition, other regulatory proteins such as ZEB1 could be added to the next generation model.
ZEB1 can activate the expression of mesenchymal genes such as collagens, smooth muscle actin and myosin, Vimentin while simultaneously contributing
to the repression of epithelial genes \cite{Liu:2008aa}.
Therefore, ZEB1 can act in parallel to SNAIL and is an alternative to the canonical signaling paradigm presented here.
Hong et al. developed an ODE model of ZEB1 signaling in MCF10A cells which also demonstrated intermediate EMT states \cite{Hong:2015aa}.
Thus, there may be alternative modes resulting in a hybrid phenotype that should be included in future model architecture.
Lastly, while we have modeled classical protein signaling, we have not considered the role of regulatory RNAs on EMT.
There is growing evidence that microRNAs (miRNAs) play a strong role in EMT, where several miRNAs,
for example miR-21 and miR-31 are strongly associated with TGF-$\beta$ exposure \cite{Bullock:2012aa}, and have suggested that
the EMT process is driven by a miR-34/SNAIL and/or miR-200/ZEB feedback circuit \cite{Lu:2013aa,Zhang:2014aa,Tian:2013aa}.
Addressing missing structural components like these (and potentially others), could generate more insight into TGF-$\beta$ signaling and its role in phenotypic transformation.
